\begin{conclusion}

    The goal of this thesis was to design and create a proof-of-concept for the library for the .NET, that would be able to map objects into grapghs
    and vice versa with the ability to execute queries on the Neo4j graph database.

    At the begging of this thesis, we studied graph databases, their properties and their differences from the relational databases.
    We also studied the C\# language and .NET with the aim to understand how LINQ library works.

    With the understaning of both the language and the database system we looked into a similar solutins, first one was the
    Entity Framework, which is \acrshort{orm} library for the .NET. The second was the Neo4j-\acrshort{ogm} library for the Java.

    Having studied both technologies and existings solutions, we defined our goals for the design of the library. Based on these goals
    we created a desing for our library.

    Using the design we created, we implemented proof-of-concept for the library. The proof-of-concept has beed tested using \acrshort{tdd}
    principles. This library has limited functionality, but it proves the posibility of the translation between LINQ and Cypher queries.
    At the end of the implementation we prepared our project for the release with creating of GitHub actions providing us the \acrshort{cicd}
    capabilities.

    At last we evaluated our solution, which met all the proposed goals of the implementation of the proof-of-concept.
    However, we pointed out the oversights in our design and proposed next steps for the library.
    With these steps implemented, the library should be ready for the use in the production envirnoment.


\end{conclusion}